Supporting Ecological Decision Making Using Feature-Selection and Variable Importance

### 2020-03-23 docs/00-manuscripts/ieee/ieee-manuscript.tex
upd appendices spacing, upd table width

% filter methods
\begin{table}[b!]
\centering
\caption[t]{List of filter methods used in this work}
\begingroup\footnotesize
\begin{adjustbox}{width={0.48\textwidth},totalheight={\textheight},keepaspectratio}
	\begin{tabular}{lll}
		\\
		Name                                         & Group                             & Reference          \\
		\toprule
		Linear correlation (Pearson)                 & univariate, linear, correlation   & \cite{pearson1901} \\
		Information gain                             & univariate, non-linear, entropy   & \cite{quinlan1986} \\
		Minimum redundancy, maximum relevance        & multivariate, non-linear, entropy & \cite{zhao2013}    \\
		Carscore                                     & multivariate, linear, correlation & \cite{zuber2011}   \\
		Relief                                       & multivariate, linear, entropy,    & \cite{kira1992}    \\
		Conditional minimal information maximization & multivariate, linear, entropy     & \cite{fleuret2004}
	\end{tabular}
\end{adjustbox}
\endgroup\label{tab:filter-methods}
\end{table}

@@

In this work we applied permutation-based feature importance and \ac{ALE} plots to calculate feature importance for the HR dataset.
With the limitations of both methods in mind we aimed to get a general overview of the feature importance of the hyperspectral bands while keeping modest on over-interpreting the results.
We used the algorithm which showed the best performance for the HR (SVM) task to calculate the feature importance.

@@

\subsubsection{ALE plots}

In addition to permutation-based variable importance, \ac{ALE} plots were used to analyze the importance of features.
ALE plots

@@

\subsubsection{Variable importance vs.\ filter methods}

WIP

\subsubsection{Ecological Interpretation}

% TODO: talk about the link to RS spectra

>>>>

% filter methods
\begin{table}[b!]
\centering
\caption[t]{List of filter methods used in this work}
\begingroup\footnotesize
\begin{adjustbox}{width={0.48\textwidth},totalheight={\textheight},keepaspectratio}
	\begin{tabular}{lll}
		\\
		Name                                         & Group                             & Ref.               \\
		\toprule
		Linear correlation (Pearson)                 & univariate, linear, correlation   & \cite{pearson1901} \\
		Information gain                             & univariate, non-linear, entropy   & \cite{quinlan1986} \\
		Minimum redundancy, maximum relevance        & multivariate, non-linear, entropy & \cite{zhao2013}    \\
		Carscore                                     & multivariate, linear, correlation & \cite{zuber2011}   \\
		Relief                                       & multivariate, linear, entropy,    & \cite{kira1992}    \\
		Conditional minimal information maximization & multivariate, linear, entropy     & \cite{fleuret2004}
	\end{tabular}
\end{adjustbox}
\endgroup\label{tab:filter-methods}
\end{table}

@@

In this work we applied permutation-based feature importance and \ac{ALE} plots to calculate feature importance for the HR dataset.
With the limitations of both methods in mind we aimed to get a general overview of the feature importance of the hyperspectral bands while keeping modest on over-interpreting the results.
We used the algorithm which showed the best performance for the HR (SVM) task to calculate the feature importance.
ALE plots were not discussed in greater detail and are available as supplementarty material.

@@

@@

\subsubsection{Linking feature importance to spectral characteristics}

Not surpringly the most important features for both HR and VI datasets were identified around the red egde of the spectra, specifically in the range of 700 nm to 750 nm.

FIXME: Add ref
This area has the highest ability to distinguish between reflectances related to a high density / high healthiness of vegetation and its opposite.
It is also worth mentioning that four out of ten of the most important features of dataset HR lie between 920 nm and 1000 nm.
Looking at the spectral curves of the plots, we can observe quite some variance in this area, especially for Oiartzun, which might explain why these features were considered as important by the model.
